Modeling tabular icebergs coupled to an ocean model

### 2017-03-22 JAMES_iceberg_only.tex
Lots of the files

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg_calved.png}
\caption{ {Results of the tabular-iceberg-calving experiment 30 days after the iceberg calves. The three panels show snapshots of the (a) melt rate, (b) top-of-ocean temperature and (c) $u^{*}$ at the base of the ice shelf. Fields are only shown in regions where the ice area fraction is $\geq 0.8$.}
\label{fig:Collapse_solo_melt}}
\end{center}
\end{figure}
 \clearpage

@@

 %\end{article}
 \clearpage 
%\section{Extra Figure:}
% \clearpage 
\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/three_melt_melt_m_per_year.png}
\caption{ {Results of the tabular-iceberg-calving experiment using three different melt-rate parametrization. Panels show snapshots of the melt rate 30 days after calving for simulations using the (a) three-equation melt-rate  parametrization, (b) icebergs-drift melt-rate parametrization, (c) mixed-melt-rate parametrization (as described in Section 2.5.)}
\label{fig:threemelt}}
\end{center}
\end{figure}
 \clearpage

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/ALE_z_static_shelf_solo_melt_m_per_year_sst_ustar_iceberg_calved.png}
\caption{ {Results of the tabular-iceberg-calving experiment 30 days after the iceberg calves. The three panels show snapshots of the (a) melt rate, (b) top-of-ocean temperature and (c) $u^{*}$ at the base of the ice shelf. Ocean grid cells without ice cover are shown in grey.}
\label{fig:Collapse_solo_melt}}
\end{center}
\end{figure}
 \clearpage

@@

 %\end{article}
 \clearpage 
%\section{Extra Figure:}
% \clearpage 
\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/three_melt_melt_m_per_year.png}
\caption{ {Results of the tabular-iceberg-calving experiment using three different melt-rate parametrization. Panels show snapshots of the melt rate 30 days after calving for simulations using the (a) three-equation melt-rate  parametrization, (b) icebergs-drift melt-rate parametrization, (c) mixed-melt-rate parametrization (as described in Section 2.5.). Ocean grid cells without ice cover are shown in grey.}
\label{fig:threemelt}}
\end{center}
\end{figure}
 \clearpage
